### 2013-07-31 3/sar.tex
Final changes before submission to Alan???

This chapter  highlights that SAR
                data are heteroskedastic in the original domain.
Relying solely on statistical and mathematical principles,             
the log-transformed SAR data is shown to be homoskedastic.
From there, the consistent sense of variance and a few consistent measures of distance are proposed and validated against real-life
                practical SAR data.

@@

\begin{table}
\centering

%awk -F"&" '{print $4}' tmp.0.txt | awk -F"(" '{print $1}'
\begin{tabular}{c|c|c|c|c|c}
No  & 70\%            &75\%             &80\%             &85\%             &90\%\\
\hline
2   &2.9024 (0.0252)  &3.7088 (0.0261)  &4.7960 (0.0327)  &6.3488 (0.0242)  &8.7974 (0.0370)\\
3   &3.4698 (0.0141)  &4.1308 (0.0177)  &4.9585 (0.0245)  &6.1176 (0.0136)  &7.9207 (0.0316)\\
4   &3.6505 (0.0225)  &4.2096 (0.0386)  &4.9392 (0.0347)  &5.9195 (0.0341)  &7.4209 (0.0162)\\
5   &3.7421 (0.0134)  &4.2513 (0.0165)  &4.8967 (0.0297)  &5.7729 (0.0170)  &7.0725 (0.0250)\\
6   &3.7850 (0.0149)  &4.2588 (0.0242)  &4.8611 (0.0160)  &5.6449 (0.0162)  &6.8062 (0.0282)\\
7   &3.8274 (0.0119)  &4.2686 (0.0102)  &4.8179 (0.0117)  &5.5447 (0.0114)  &6.6049 (0.0158)\\
8   &3.8468 (0.0110)  &4.2591 (0.0124)  &4.7747 (0.0176)  &5.4519 (0.0087)  &6.4370 (0.0085)\\
9   &3.8610 (0.0081)  &4.2503 (0.0125)  &4.7430 (0.0120)  &5.3688 (0.0085)  &6.2829 (0.0112)\\
10  &3.8663 (0.0089)  &4.2423 (0.0126)  &4.6967 (0.0102)  &5.3015 (0.0103)  &6.1574 (0.0116)\\
11  &3.8707 (0.0089)  &4.2284 (0.0109)  &4.6693 (0.0078)  &5.2387 (0.0111)  &6.0473 (0.0122)\\
12  &3.8763 (0.0063)  &4.2228 (0.0072)  &4.6370 (0.0139)  &5.1805 (0.0050)  &5.9502 (0.0044)\\
13  &3.8808 (0.0048)  &4.2089 (0.0083)  &4.6096 (0.0055)  &5.1315 (0.0092)  &5.8654 (0.0070)\\
14  &3.8761 (0.0048)  &4.1920 (0.0112)  &4.5816 (0.0069)  &5.0845 (0.0058)  &5.7870 (0.0106)\\
15  &3.8806 (0.0048)  &4.1901 (0.0063)  &4.5592 (0.0088)  &5.0372 (0.0076)  &5.7158 (0.0119)\\
16  &3.8774 (0.0032)  &4.1778 (0.0060)  &4.5397 (0.0049)  &4.9985 (0.0087)  &5.6483 (0.0083)\\
17  &3.8760 (0.0043)  &4.1682 (0.0035)  &4.5149 (0.0060)  &4.9652 (0.0051)  &5.5919 (0.0078)\\
18  &3.8708 (0.0083)  &4.1584 (0.0026)  &4.4951 (0.0030)  &4.9273 (0.0043)  &5.5319 (0.0083)\\
19  &3.8694 (0.0055)  &4.1464 (0.0037)  &4.4755 (0.0039)  &4.8961 (0.0027)  &5.4838 (0.0031)\\
20  &3.8687 (0.0051)  &4.1364 (0.0041)  &4.4555 (0.0072)  &4.8673 (0.0042)  &5.4371 (0.0076)\\
21  &3.8672 (0.0064)  &4.1268 (0.0049)  &4.4401 (0.0052)  &4.8360 (0.0045)  &5.3927 (0.0027)\\
22  &3.8637 (0.0046)  &4.1215 (0.0037)  &4.4253 (0.0050)  &4.8136 (0.0043)  &5.3499 (0.0060)\\
23  &3.8610 (0.0032)  &4.1110 (0.0039)  &4.4093 (0.0057)  &4.7870 (0.0059)  &5.3118 (0.0056)\\
24  &3.8571 (0.0033)  &4.1015 (0.0051)  &4.3942 (0.0060)  &4.7650 (0.0026)  &5.2732 (0.0054)\\
25  &3.8541 (0.0054)  &4.0931 (0.0052)  &4.3803 (0.0032)  &4.7416 (0.0024)  &5.2453 (0.0045)
\end{tabular}

@@

\textbf{In summary}, a few measurements of distance, being dispersion and contrast, are shown to agree with the consistent sense of variance and homoskedasticity.
The dispersion measurement can be used to test 
if a pixel belongs to a ``known'' class of physical scatterer.
The consistent sense of contrast can be used to test if any pair of measured data points belong to  the same homogeneous class.
An example application of this is described in our fMLE speckle filter.
The consistent sense 
of contrast also gives rise to consistent measures of sample variances, which for example, can be used to test 
if a group of pixels can form a homogeneous area.
%All of these applications are presented in chapter \ref{chap:applications}
Chapter \ref{chap:applications} presents several of these applications which further validates the models proposed herein.

>>>>

This chapter  highlights that SAR
                data are heteroskedastic in the original domain.
Relying solely on statistical and mathematical principles,             
the log-transformed SAR data is then shown to be homoskedastic.
From there, the consistent sense of variance and a few consistent measures of distance are proposed and validated against real-life
                practical SAR data.

@@

\begin{table}[H]
\centering
\small
%awk -F"&" '{print $4}' tmp.0.txt | awk -F"(" '{print $1}'
\begin{tabular}{c|c|c|c|c|c}
No  & 70\%            &75\%             &80\%             &85\%             &90\%\\
\hline
2   &2.9024 (0.0252)  &3.7088 (0.0261)  &4.7960 (0.0327)  &6.3488 (0.0242)  &8.7974 (0.0370)\\
3   &3.4698 (0.0141)  &4.1308 (0.0177)  &4.9585 (0.0245)  &6.1176 (0.0136)  &7.9207 (0.0316)\\
4   &3.6505 (0.0225)  &4.2096 (0.0386)  &4.9392 (0.0347)  &5.9195 (0.0341)  &7.4209 (0.0162)\\
5   &3.7421 (0.0134)  &4.2513 (0.0165)  &4.8967 (0.0297)  &5.7729 (0.0170)  &7.0725 (0.0250)\\
6   &3.7850 (0.0149)  &4.2588 (0.0242)  &4.8611 (0.0160)  &5.6449 (0.0162)  &6.8062 (0.0282)\\
7   &3.8274 (0.0119)  &4.2686 (0.0102)  &4.8179 (0.0117)  &5.5447 (0.0114)  &6.6049 (0.0158)\\
8   &3.8468 (0.0110)  &4.2591 (0.0124)  &4.7747 (0.0176)  &5.4519 (0.0087)  &6.4370 (0.0085)\\
9   &3.8610 (0.0081)  &4.2503 (0.0125)  &4.7430 (0.0120)  &5.3688 (0.0085)  &6.2829 (0.0112)\\
10  &3.8663 (0.0089)  &4.2423 (0.0126)  &4.6967 (0.0102)  &5.3015 (0.0103)  &6.1574 (0.0116)\\
11  &3.8707 (0.0089)  &4.2284 (0.0109)  &4.6693 (0.0078)  &5.2387 (0.0111)  &6.0473 (0.0122)\\
12  &3.8763 (0.0063)  &4.2228 (0.0072)  &4.6370 (0.0139)  &5.1805 (0.0050)  &5.9502 (0.0044)\\
13  &3.8808 (0.0048)  &4.2089 (0.0083)  &4.6096 (0.0055)  &5.1315 (0.0092)  &5.8654 (0.0070)\\
14  &3.8761 (0.0048)  &4.1920 (0.0112)  &4.5816 (0.0069)  &5.0845 (0.0058)  &5.7870 (0.0106)\\
15  &3.8806 (0.0048)  &4.1901 (0.0063)  &4.5592 (0.0088)  &5.0372 (0.0076)  &5.7158 (0.0119)\\
16  &3.8774 (0.0032)  &4.1778 (0.0060)  &4.5397 (0.0049)  &4.9985 (0.0087)  &5.6483 (0.0083)\\
17  &3.8760 (0.0043)  &4.1682 (0.0035)  &4.5149 (0.0060)  &4.9652 (0.0051)  &5.5919 (0.0078)\\
18  &3.8708 (0.0083)  &4.1584 (0.0026)  &4.4951 (0.0030)  &4.9273 (0.0043)  &5.5319 (0.0083)\\
19  &3.8694 (0.0055)  &4.1464 (0.0037)  &4.4755 (0.0039)  &4.8961 (0.0027)  &5.4838 (0.0031)\\
20  &3.8687 (0.0051)  &4.1364 (0.0041)  &4.4555 (0.0072)  &4.8673 (0.0042)  &5.4371 (0.0076)\\
21  &3.8672 (0.0064)  &4.1268 (0.0049)  &4.4401 (0.0052)  &4.8360 (0.0045)  &5.3927 (0.0027)\\
22  &3.8637 (0.0046)  &4.1215 (0.0037)  &4.4253 (0.0050)  &4.8136 (0.0043)  &5.3499 (0.0060)\\
23  &3.8610 (0.0032)  &4.1110 (0.0039)  &4.4093 (0.0057)  &4.7870 (0.0059)  &5.3118 (0.0056)\\
24  &3.8571 (0.0033)  &4.1015 (0.0051)  &4.3942 (0.0060)  &4.7650 (0.0026)  &5.2732 (0.0054)\\
25  &3.8541 (0.0054)  &4.0931 (0.0052)  &4.3803 (0.0032)  &4.7416 (0.0024)  &5.2453 (0.0045)
\end{tabular}

@@

In summary, a few measurements of distance, being dispersion and contrast, are shown to agree with the consistent sense of variance and homoskedasticity.
The dispersion measurement can be used to test 
if a pixel belongs to a ``known'' class of physical scatterer.
The consistent sense of contrast can be used to test if any pair of measured data points belong to  the same homogeneous class.
An example application of this is described in our fMLE speckle filter.
The consistent sense 
of contrast also gives rise to consistent measures of sample variances, which for example, can be used to test 
if a group of pixels can form a homogeneous area.
%All of these applications are presented in chapter \ref{chap:applications}
Chapter \ref{chap:applications} presents several of these applications which further validates the models proposed herein.

### 2013-07-31 4/polsar.tex
Final changes before submission to Alan???

Its log-transformed variable consequently 
  behaves like a summation of $d$ log-chi-squared random variables with the same degrees of freedom  
\begin{equation}
\label{eqn:sum_log_chi_squared_rv}
\caption{eqn:Logarithm of Determinant Ratio and the Sum of Log-Chi-Squared Distributions}
\Lambda^d_L = ln \left[ (2L)^d \frac{|C_v|}{|\Sigma_v|} \right] \sim \sum_{i=0}^{d-1} \Lambda^\chi (2L-2i)
\end{equation}
with
  $\Lambda^\chi (k) \sim \ln \left[ \chi^2 (k) \right]$

@@

Since the average and variance of both chi-squared distribution and log-chi-squared distribution are constant,
  the product and summation of these random variables also has fixed summary statistics.
Specifically:
\begin{eqnarray*}
  avg \left[ \prod^{d-1}_{i=0} \chi^2(2L-2i) \right] &=& 2^d \cdot \prod^{d-1}_{i=0} (L-i), \\
  var \left[ \prod^{d-1}_{i=0} \chi^2(2L-2i) \right] &=& \prod^{d-1}_{i=0} 4(L-i)(L-i+1) - \prod^{d-1}_{i=0} 4(L-i)^2, \\
  avg \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &=& d \cdot \ln{2} + \sum^{d-1}_{i=0} \psi^0(L-i), \\
  var \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &=& \sum^{d-1}_{i=0} \psi^1(L-i)
\end{eqnarray*}

@@

The results so far for our models can be summarized as:
\begin{align*}
  \mathbb{R} &= \frac{|C_v|}{|\Sigma_v|} \sim \frac{1}{(2L)^d} \prod^{d-1}_{i=0} \chi^2(2L-2i) \\% \label{eqn:polsar_ratio_det_cov_dist} \\
  \mathbb{L} &= \ln{|C_v|} - \ln{|\Sigma_v|} \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \\ %\label{eqn:polsar_dispersion_log_det_cov_dist} \\
  \mathbb{D} &= \ln{|C_v|} - avg(\ln{|C_v|}) \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \ln{2} + k\\
  \mathbb{C} &= \ln{|C_{1v}|} - \ln{|C_{2v}|} \sim \sum^{d-1}_{i=0} \Delta(2L-2i) \\
  \mathbb{A} &= avg(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \\ %\label{eqn:polsar_dispersion_averages} \\
  \mathbb{V} &= var(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^1(L-i) \\ %\label{eqn:polsar_dispersion_variance} \\
  \mathbb{E} &= mse(\mathbb{L}) =\left[ \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \right]^2 +  \sum^{d-1}_{i=0} \psi^1(L-i) %\label{eqn:polsar_dispersion_mse} 
\end{align*}

Upon setting d = 1 into the above models,
  Section \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results
are consistent with not only the following results for single-look SAR derived earlier, i.e. $d =1,  L = 1$,
\begin{align*}
  I &\sim \bar{I} \cdot pdf \left[ e^{-R} \right] \\
  \log_2{I} &\sim \log_2{\bar{I}} + pdf \left[ 2^xe^{-2^x}\ln2 \right] \\
  \mathbb{R} &= \frac{I}{\bar{I}} \sim pdf \left[ e^{-x} \right]  \\
  \mathbb{L} &= \log_2{I} - \log_2{\bar{I}} \sim pdf \left[ 2^xe^{-2^x}\ln2 \right]\\
  \mathbb{D} &= \log_2{I} - avg(\log_2{I}) \sim pdf \left[ e^{-(2^xe^{-\gamma})} 2^xe^{-\gamma} \ln2 \right] \\
  \mathbb{C} &= \log_2{I_1} - \log_2{I_2} \sim pdf \left[ \frac{2^x}{(1+2^x)^2} \ln2 \right] \\
  \mathbb{A} &= avg(\mathbb{L}) = -\gamma / \ln{2} \\
  \mathbb{V} &= var(\mathbb{L}) = \frac{\pi^2}{6} \frac{1}{ \ln^2{2}} \\
  \mathbb{E} &= mse(\mathbb{L}) = \frac{1}{\ln^2{2}}( \gamma^2 + \pi^2/6 ) = 4.1161 
\end{align*}
but also the following well-known results for multi-look SAR, i.e. $d=1,L>1$:
  \begin{align*}
I &\sim pdf \left[ \frac{L^L x^{L-1} e^{-Lx/\bar{I}}}{\Gamma(L) \bar{I}^L} \right] \\
N = \ln{I} &\sim pdf \left[ \frac{L^L}{\Gamma(L)} e^{L(x-\bar{N})-Le^{x-\bar{N}}} \right]
  \end{align*}
Furthermore, the following results for multi-look SAR data, which can be thought of
either as extensions of the corresponding single-look SAR results or as simple cases of
the POLSAR results can also be derived and shown to be as follows:

@@

\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[part-pol (2x2) dispersion]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
                 \epsffile{images/verify_polsar_2x2_dispersion_distribution.eps} 
		 \label{dispersion_2x2}
	} 
	\hfill	
	\subfloat[part-pol (2x2) contrast]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/verify_polsar_2x2_contrast_distribution.eps} 	
		 \label{contrast_2x2}
	} \\
	\subfloat[full-pol (3x3) dispersion]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
                 \epsffile{images/verify_polsar_3x3_dispersion_distribution.eps} 
		 \label{dispersion_3x3}
	} 
	\hfill	
	\subfloat[full-pol (3x3) contrast]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/verify_polsar_3x3_contrast_distribution.eps} 	
		 \label{contrast_3x3}
	}
\end{tabular}
\caption{Validating the dispersion and contrast models against both partial and full polarimetric AIRSAR Flevoland data.}
\label{fig:verify_polsar_2x2_simulation_dispersion_contrast}
\end{figure}

@@

There are two main ``imperfections'' that are usually found in practical POLSAR data with reference to the theoretical model.
The first is the mutually independent assumption for each component in the POLSAR target vector $s$.
However, in practice, high correlation is routinely observable between the POLSAR data components,
  specifically between $S_{hh}$ and $S_{vv}$.
This phenomena is also present in our AIRSAR dataset, where $\Sigma_v = avg(C_v) = \begin{vmatrix} 0.0084 & 1 \cdot 10^{-6} + 4 \cdot 10^{-4} i & 0.0071 - 0.0017 i \\ 1 \cdot 10^{-6} - 4 \cdot 10^{-4} i & 0.0017 & -3 \cdot 10^{-4} - 2 \cdot 10^{-4} i \\ 0.0071 + 0.0017 i & -3 \cdot 10^{-4} + 2 \cdot 10^{-4} i & 0.0122 \end{vmatrix}$.
Despite the mismatch, the proposed model  is still valid under such conditions, as observed in the part-pol (HH-VV) and full-pol
plots in Figs. \ref{fig:verify_polsar_2x2_simulation_dispersion_contrast} to \ref{fig:verify_polsar_2x2_simulation_det}.

@@

In \textbf{summary}, this chapter proposes the determinant of the POLSAR covariance matrix as the scalar and representative observable for the both partial and full polarimetric SAR data.
Out of many different scalar projections of the multi-dimensional POLSAR data, this observable is proposed together with its underlying statistical model, from which consistent discriminant measures are also proposed.
The derived models are shown to be heteroskedastic in the original domain, and logarithmic transformation is shown to convert these into homoskedastic models.
The representative power of the observable is explained in a few different ways.
Firstly, the determinant observable neatly transforms into the representative and widely-used SAR intensity when the dimensional number is collapsed to one, putting the commonly-used statistical models for SAR intensity to fall within this generic proposed models.
Secondly, this observable is also  widely used in existing discrimination measures for POLSAR.
In fact, this chapter also proposes several new discrimination measures for POLSAR,
  which together with the proposed statistical models help to link the existing discriminant measures for POLSAR to the widely-used intensity ratio for SAR.
Thus this theory should help in a wide range of applications, where a single scalar observable is required to represent the complex, multi-dimensional and inter-correlated POLSAR data.
It also builds a bridge allowing  certain existing classes of SAR data processing technique to be applicable towards POLSAR data.
%Such applications are briefly explored in the next chapter. 
The next chapter will briefly explore such applications as well as presents further validation of the proposed models.

>>>>

Its log-transformed variable consequently 
  behaves like a summation of $d$ log-chi-squared random variables with the same degrees of freedom  
\begin{equation}
\label{eqn:sum_log_chi_squared_rv}
\caption{eqn:Logarithm of Determinant Ratio and the Sum of Log-Chi-Squared Distributions}
\Lambda^d_L = ln \left[ (2L)^d \frac{|C_v|}{|\Sigma_v|} \right] \sim \sum_{i=0}^{d-1} \Lambda^\chi (2L-2i)
\end{equation}
where $\Lambda^\chi (k) \sim \ln \left[ \chi^2 (k) \right]$

@@

Since the average and variance of both chi-squared distribution and log-chi-squared distribution are constant,
  the product and summation of these random variables also has fixed summary statistics.
Specifically:

\begin{eqnarray*}
  avg \left[ \prod^{d-1}_{i=0} \chi^2(2L-2i) \right] &=& 2^d \cdot \prod^{d-1}_{i=0} (L-i), \\
  var \left[ \prod^{d-1}_{i=0} \chi^2(2L-2i) \right] &=& \prod^{d-1}_{i=0} 4(L-i)(L-i+1) - \prod^{d-1}_{i=0} 4(L-i)^2, \\
  avg \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &=& d \cdot \ln{2} + \sum^{d-1}_{i=0} \psi^0(L-i), \\
  var \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &=& \sum^{d-1}_{i=0} \psi^1(L-i)
\end{eqnarray*}

@@

The results so far for our models can be summarized as:
{\footnotesize
\begin{align*}
  \mathbb{R} &= \frac{|C_v|}{|\Sigma_v|} \sim \frac{1}{(2L)^d} \prod^{d-1}_{i=0} \chi^2(2L-2i) \\% \label{eqn:polsar_ratio_det_cov_dist} \\
  \mathbb{L} &= \ln{|C_v|} - \ln{|\Sigma_v|} \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \\ %\label{eqn:polsar_dispersion_log_det_cov_dist} \\
  \mathbb{D} &= \ln{|C_v|} - avg(\ln{|C_v|}) \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \ln{2} + k\\
  \mathbb{C} &= \ln{|C_{1v}|} - \ln{|C_{2v}|} \sim \sum^{d-1}_{i=0} \Delta(2L-2i) \\
  \mathbb{A} &= avg(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \\ %\label{eqn:polsar_dispersion_averages} \\
  \mathbb{V} &= var(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^1(L-i) \\ %\label{eqn:polsar_dispersion_variance} \\
  \mathbb{E} &= mse(\mathbb{L}) =\left[ \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \right]^2 +  \sum^{d-1}_{i=0} \psi^1(L-i) %\label{eqn:polsar_dispersion_mse} 
\end{align*}
}%

Upon setting d = 1 into the above models,
  Section \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results
are consistent with not only the following results for single-look SAR derived earlier, i.e. $d =1,  L = 1$,

{\footnotesize
\begin{align*}  
  I &\sim \bar{I} \cdot pdf \left[ e^{-R} \right] \\
  \log_2{I} &\sim \log_2{\bar{I}} + pdf \left[ 2^xe^{-2^x}\ln2 \right] \\
  \mathbb{R} &= \frac{I}{\bar{I}} \sim pdf \left[ e^{-x} \right]  \\
  \mathbb{L} &= \log_2{I} - \log_2{\bar{I}} \sim pdf \left[ 2^xe^{-2^x}\ln2 \right]\\
  \mathbb{D} &= \log_2{I} - avg(\log_2{I}) \sim pdf \left[ e^{-(2^xe^{-\gamma})} 2^xe^{-\gamma} \ln2 \right] \\
  \mathbb{C} &= \log_2{I_1} - \log_2{I_2} \sim pdf \left[ \frac{2^x}{(1+2^x)^2} \ln2 \right] \\
  \mathbb{A} &= avg(\mathbb{L}) = -\gamma / \ln{2} \\
  \mathbb{V} &= var(\mathbb{L}) = \frac{\pi^2}{6} \frac{1}{ \ln^2{2}} \\
  \mathbb{E} &= mse(\mathbb{L}) = \frac{1}{\ln^2{2}}( \gamma^2 + \pi^2/6 ) = 4.1161 
\end{align*}
}%
but also the following well-known results for multi-look SAR, i.e. $d=1,L>1$:
  \begin{align*}
I &\sim pdf \left[ \frac{L^L x^{L-1} e^{-Lx/\bar{I}}}{\Gamma(L) \bar{I}^L} \right] \\
N = \ln{I} &\sim pdf \left[ \frac{L^L}{\Gamma(L)} e^{L(x-\bar{N})-Le^{x-\bar{N}}} \right]
  \end{align*}
Furthermore, the following results for multi-look SAR data, which can be thought of
either as extensions of the corresponding single-look SAR results or as simple cases of
the POLSAR results can also be derived and shown to be as follows:

@@

\begin{figure}[bth!]
\centering
\begin{tabular}{c}
	\subfloat[part-pol (2x2) dispersion]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
                 \epsffile{images/verify_polsar_2x2_dispersion_distribution.eps} 
		 \label{dispersion_2x2}
	} 
	\hfill	
	\subfloat[part-pol (2x2) contrast]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/verify_polsar_2x2_contrast_distribution.eps} 	
		 \label{contrast_2x2}
	} \\
	\subfloat[full-pol (3x3) dispersion]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
                 \epsffile{images/verify_polsar_3x3_dispersion_distribution.eps} 
		 \label{dispersion_3x3}
	} 
	\hfill	
	\subfloat[full-pol (3x3) contrast]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/verify_polsar_3x3_contrast_distribution.eps} 	
		 \label{contrast_3x3}
	}
\end{tabular}
\caption{Validating the dispersion and contrast models against both partial and full polarimetric AIRSAR Flevoland data.}
\label{fig:verify_polsar_2x2_simulation_dispersion_contrast}
\end{figure}

@@

There are two main ``imperfections'' that are usually found in practical POLSAR data with reference to the theoretical model.
The first is the mutually independent assumption for each component in the POLSAR target vector $s$.
However, in practice, high correlation is routinely observable between the POLSAR data components,
  specifically between $S_{hh}$ and $S_{vv}$.
This phenomena is also present in our AIRSAR dataset, where
${\Sigma_v = avg(C_v) = \begin{vmatrix} 0.0084 & 1 \cdot 10^{-6} + 4 \cdot 10^{-4} i & 0.0071 - 0.0017 i \\ 1 \cdot 10^{-6} - 4 \cdot 10^{-4} i & 0.0017 & -3 \cdot 10^{-4} - 2 \cdot 10^{-4} i \\ 0.0071 + 0.0017 i & -3 \cdot 10^{-4} + 2 \cdot 10^{-4} i & 0.0122 \end{vmatrix}}$.
Despite the mismatch, the proposed model  is still valid under such conditions, as observed in the part-pol (HH-VV) and full-pol
plots in Figs. \ref{fig:verify_polsar_2x2_simulation_dispersion_contrast} to \ref{fig:verify_polsar_2x2_simulation_det}.

@@

In summary, this chapter proposes the determinant of the POLSAR covariance matrix as the scalar and representative observable for the both partial and full polarimetric SAR data.
Out of many different scalar projections of the multi-dimensional POLSAR data, this observable is proposed together with its underlying statistical model, from which consistent discriminant measures are also proposed.
The derived models are shown to be heteroskedastic in the original domain, and logarithmic transformation is shown to convert these into homoskedastic models.
The representative power of the observable is explained in a few different ways.
Firstly, the determinant observable neatly transforms into the representative and widely-used SAR intensity when the dimensional number is collapsed to one, putting the commonly-used statistical models for SAR intensity to fall within this generic proposed models.
Secondly, this observable is also  widely used in existing discrimination measures for POLSAR.
In fact, this chapter also proposes several new discrimination measures for POLSAR,
  which together with the proposed statistical models help to link the existing discriminant measures for POLSAR to the widely-used intensity ratio for SAR.
Thus this theory should help in a wide range of applications, where a single scalar observable is required to represent the complex, multi-dimensional and inter-correlated POLSAR data.
It also builds a bridge allowing  certain existing classes of SAR data processing technique to be applicable towards POLSAR data.
%Such applications are briefly explored in the next chapter. 
The next chapter will briefly explore such applications as well as presents further validation of the proposed models.
